\documentclass[10pt, letterpaper]{article}
\usepackage[a4paper, margin=0.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{inconsolata}
\usepackage{stmaryrd}
\usepackage{hyperref}
\renewcommand*\familydefault{\ttdefault}
\usepackage[T1]{fontenc}
\usepackage{ragged2e}
\definecolor{purduegold}{RGB}{170, 140, 0}

\newcommand{\emphasis}[1]{
    \textcolor{purduegold}{\textbf{#1}}
}

\newcommand{\Emphasis}[1]{\uppercase{\textbf{#1}}}

\newcommand{\EMPHASIS}[1]{
    \uppercase{\emphasis{#1}}
}

\newcommand\bars{\leavevmode\xleaders\hbox{-}\hfill\kern0pt}

\title{
    \vspace{-10mm}
    {\Huge {\href{https://www.linkedin.com/in/EthanDCampbell}{Ethan.\textbf{Campbell}}}}\\
    %{\small 341 Smiley St. West Lafayette, IN 47906 \hspace{10pt} (765)-438-5553}\\
    {\small 
        [{
            \emphasis{ethan.d.campbell@outlook.com}, \hspace{10pt} 
            \emphasis{(765)438-5553}, \hspace{10pt} 
            \href{http://www.linkedin.com/in/EthanDCampbell}{\emphasis{linkedin.com/in/EthanDCampbell}}
        }]
    }\\
    {\normalsize 
        /*------------------------------------
        Master's student specializing in machine learning and embedded systems
        ------------------------------------*/
    }
}
\date{} %omit the date line
\begin{document}

\maketitle
\vspace{-20mm}
\section*{\huge{//Experience - Internships}}
    \subsection*{\Emphasis{Milwaukee Tool}; \emphasis{Firmware Engineering;} Summer 2021}
        \begin{enumerate}[label={[\arabic*]}]
            \setcounter{enumi}{-1}
            \item Developed a firmware analysis tool to extract run time data without compiling source or deploying firmware executables. Deployed into CI/CD pipeline for seamless integration with firmware development. [{\scriptsize \EMPHASIS{Python}}]
            \item Developed a circular buffer firmware module and driver for infinite data logging and retrieval to an eternal flash SPI IC. Extensibility and modularity primary factors for design. [{\scriptsize\EMPHASIS{C}}]
        \end{enumerate}
    \subsection*{\Emphasis{Garmin}; \emphasis{Software Engineering;} Summer 2019}
        \begin{enumerate}[label={[\arabic*]}]
            \setcounter{enumi}{-1}
            \item Developed and deployed Software Quality tools, which improved workflow and efficiency of global teams. Central management \& analysis with networked background watchers on test benches. See \textbf{Projects[2]}\\ {\scriptsize [\EMPHASIS{C\#}, \EMPHASIS{.NET}, \EMPHASIS{WMI}]}
        \end{enumerate}
    \subsection*{\Emphasis{Aptiv}; \emphasis{Systems Engineering;} Summer 2018}
        \begin{enumerate}[label={[\arabic*]}]
            \setcounter{enumi}{-1}
            \item Root cause failure analysis for automotive systems, which progressed the development of new products. 
            \item Evaluated CAN protocol communication and improved errant equipment behavior, which resulted in faster product validation methods. {\scriptsize [\EMPHASIS{CAN}]}
        \end{enumerate}
    \subsection*{\Emphasis{Delphi}; \emphasis{Production Control and Logistics;} Summer 2017}
        \begin{enumerate}[label={[\arabic*]}]
            \setcounter{enumi}{-1}
            \item Developed factory information dashboard, which resulted in better inventory and production management.\\ {[{\scriptsize \EMPHASIS{Java, Apache, Bootstrap}}]}
        \end{enumerate}
\section*{\huge{//Education :\emphasis{Purdue University}}}
    \subsection*{May 2021; Bachelor's - Computer Engineering}
        \begin{enumerate}[label={[\arabic*]}]
            \setcounter{enumi}{-1}
            \item \emphasis{3.7 GPA} | Eta Kappa Nu (HKN) : IEEE Honor Society $\rightarrowtriangle$ Operations Director - Executive
            \item \emphasis{UTA} ECE 404 Computer Security | 14 hr/wk | instructed and debugged python
        \end{enumerate}
    \subsection*{May 2023; Master's - Electrical and Computer Engineering}
        \begin{enumerate}[label={[\arabic*]}]
            \setcounter{enumi}{-1}
            \item \emphasis{GTA} ECE 463 Computer Networks | 20 hr/wk | course coordination, UTA supervision, office hours
        \end{enumerate}
\section*{\huge{//Skills}}
    \begin{enumerate}[label={[\arabic*]}]
        \setcounter{enumi}{-1}
        \item \emphasis{C} \& \emphasis{C++}\hspace{10pt}[ARM Firmware, Computer Vision, SQ Network Monitoring App, Lightweight Web Server, RTOS]\\
            \hspace*{1in}{Frameworks $\rightarrowtriangle$ [OpenCV, QT, CUDA, libArgus]}
        \item \emphasis{Python}\hspace{26pt}[Deep Learning, ML, Firmware Source Analytics, Network Applications, Image Processing App]\\
            \hspace*{1in}{Frameworks $\rightarrowtriangle$ [Scikit, Numpy, PyTorch, Keras, OpenCV, PyQT]}
        \item \emphasis{Java \& C\#}\hspace{10pt}[Web Server + Dashboard Interface, Micro C Compiler]\\
            \hspace*{1in}{Frameworks $\rightarrowtriangle$ [Apache, Boostrap CSS, Ajax, WMI, .NET]}
        
    \end{enumerate}
% \section*{//Activities}
%     \begin{enumerate}[label={[\arabic*]}]
%         \setcounter{enumi}{-1}
%         \item HKN Operations Director: manage a student run non-for-profit coffee shop. Responsible for staffing, inventory, profitability, company relations.
%         \item Autonomous Controls team member working toward Level 4 Automation.
%     \end{enumerate}
    \vspace{-10mm}
% \section*{\huge{//Projects}}
  \section*{\huge //Projects}
    \begin{enumerate}[label={[\arabic*]}]
        \setcounter{enumi}{-1}
        \item \href{https://jpanos.github.io/ECE-477/}{\Emphasis{Senior Design}}: {Software Lead}. Developed Computer Vision system for Autonomous Pollination Drone. Used Nvidia Jetson Nano SBC and OpenCV \emphasis{C++}. Optimized with {libArgus} \& \emphasis{CUDA}. Wrote UART based communication protocol for inter-chip communication layer. Developed low-latency drone camera network stream. \href{https://jpanos.github.io/ECE-477/}{\underline{site}}
        \item \Emphasis{Mircroprocessor OS}: Wrote and implemented a low-level custom operating system written in embedded \emphasis{C}. Utilized micro peripherals to allow for keyboard input via PS/2 legacy protocol for keyboards.
        \item \Emphasis{SQ Application}: Network application in \emphasis{C\#}. Nodes on test SQ servers report to central server with diagnostics: temp, cpu, memory, storage, software versions, status, etc. Used .NET and WMI.

    \end{enumerate}
\end{document}
